Methods for Large Scale Learning to Rank

### 2014-04-04 report/Chapters/CrossBenchmarkComparison.tex
veel pijn en moeite in overzichtstabel. CCRank == CCR

\section{Evaluation Results Found in Literature}

>>>>

\section{Evaluation Results Found in Literature}
\begin{table}[!h]
\begin{tabular}{l|l|l}
AdaRank-\acs{MAP} & \acs{GP}Rank & RankAgg\ac{nDCG} \\ 
AdaRank-\acs{nDCG} & GRank\acs{RLS} & RankBoost \\ 
ADMM & GroupCE & RankCSA \\ 
Approx\acs{AP} & Group\acs{MLE} & RankDE \\ 
Approx\acs{nDCG} & IntervalRank & RankELM (pairwise) \\ 
BagBoo & \acs{IP}Rank & RankELM (pointwise) \\ 
Best Single Feature & KeepRank & Ranking Committee Perceptron \\ 
BL-MART & Kernel-\acs{PCA} & RankMGP \\ 
BoltzRank-Single & KL-\acs{CRF} & RankNet \\ 
BoltzRank-Pair & LAC-MR-OR & Rank\ac{RLS} \\ 
BT & LambdaMART & Rank\ac{SVM} \\ 
C-\acs{CRF} & LambdaNeuralRank & Rank\ac{SVM}-Primal \\ 
\acs{CA} & LambdaRank & Rank\acs{SVM}-Struct \\ 
\ac{CC}Rank & LARF & RE-QR \\ 
CoList & Linear Regression & REG-SHF-SDCG \\ 
Consistent-RankCosine & List\acs{MLE} & Regression \\ 
DCMP & ListNet & Ridge Regression \\ 
DirectRank & ListReg & RSRank \\ 
Energy\ac{nDCG} & LRUF & SmoothGrad \\ 
FBPCRank & MBP & SmoothRank \\ 
FenchelRank & MHR & SoftRank \\ 
FocusedBoost & MultiStageBoost & SortNet \\ 
FocusedNet & NewLoss & SparseRank \\ 
Focused\ac{SVM} & OWPC & \acs{SVD}-RankBoost \\ 
FPRank & PERF-\ac{MAP} & \ac{SVM}$^{\ac{MAP}}$ \\ 
FRank & PermuRank & SwarmRank \\ 
FSMRank & Q.D.\acs{KNN} & TGRank \\ 
FSM$^{\acs{MAP}}$ & RandomForest & TM \\ 
GAS-E & Rank-PMBGP & VFLR \\ 
\end{tabular}
\caption{Learning-to-Rank algorithms with measurements on benchmark datasets}
\label{ltr_methods_used}
\end{table}
